---
title: "machine learning project"
date: "June 21, 2015"
output: html_document
---


Introduction
-------
The study aims to use a trained model to predict the types of collected movement actions.

The model
-------
The given training data was read from the file "pml-training.csv". It was partitioned into a training and a testing subset randomly based on the variable classe with a probably 0.75. 

```{r}
setwd("/Users/ximi/Documents/coursera_datasci/prac_machine_learning")
library(caret)
set.seed(117859)
data_tr<-read.csv("pml-training.csv",fill=T,blank.lines.skip=T,na.strings=c("NA","","#DIV/0!"))
```

Variables that contain NAs over 50% of cases are removed from the data set. The column X and user_name are confounding and are forced to be taken out.
```{r}
data_tr$X<-NULL
data_tr$user_name<-NULL
na_num<-vector(mode="numeric", length=dim(data_tr)[2])
for(i in 1:dim(data_tr)[1]){
        t<-sapply(data_tr[i,], function(v) as.numeric(is.na(v)==T))
        na_num<-na_num+t
}
tmp<-which(na_num>=dim(data_tr)[1]*0.5)
data_tr<-data_tr[,-tmp]
inTrain<-createDataPartition(y=data_tr$classe,p=0.75,list=FALSE)
training<-data_tr[inTrain,]
testing<-data_tr[-inTrain,]
```

The model was trained using the random forest algorithm. The model performance using training data as input is as below in terms of a confusion matrix. 

```{r}
library(randomForest)
fitControl <- trainControl(## 10-fold CV
    method = "repeatedcv",
    number = 10,
    repeats = 10)
rf<-randomForest(classe~., data=training, importance=TRUE, proximity=TRUE, ntree=100)
rf$confusion

```
Using the testing data to predit, the accuracy and confusion matrix turns out as below.

```{r, echo=TRUE}
pred0<-predict(rf,testing)
cm<-confusionMatrix(pred0, testing$classe)
cm$overall
cm$table
```

Finally readin the seperate quiz data, the results are as below.

```{r, echo=TRUE}
data_test<-read.csv("pml-testing.csv",fill=T, blank.lines.skip=T,na.strings=c("NA","","#DIV/0!"))
data_test_1<-data_test
data_test_1$X<-NULL
data_test_1$user_name<-NULL
data_test_1<-data_test_1[,-tmp]
data_test_1$problem_id<-NULL
data_test_1$classe<-as.factor(c(rep("A",4),rep("B",4),rep("C",4),rep("D",4),rep("E",4)))

d<-rbind(testing, data_test_1)
pred2<-predict(rf,d)
tail(pred2,20)
```

 

